---
title: "Report On Big Five, Assignment 29"
author: "Maximilian Schneider"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
documentclass: report
urlcolor: blue
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    includes:
      in_header: preamble.tex
---

<!-- To render book from terminal use: Rscript -e "rmarkdown::render('big-five.Rmd')" -->

<style>
body {
text-align: justify}
.main-container {
  max-width: 1000px;
  margin-left: auto;
  margin-right: auto;
}
</style>

Abstract

# Introduction

<!-- Configuration -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width='80%',
                      include = FALSE, echo = FALSE, cache = FALSE)
```

```{r dependencies}
library(data.table)
library(purrr)
library(magrittr)
library(ggplot2); theme_set(theme_bw())
```

<!-- Data preparation -->

```{r read-data}
dt_bigf <- read.table("data.csv", header = TRUE, sep = "\t", na.strings = "") %>%
  as.data.table()
```

```{r format-data}
dt_bigf[, c("country", "education", "urban", "gender", "engnat", "hand", "religion",
            "orientation", "race", "voted", "married", "os", "browser") :=
          .(factor(country),
            factor(education, labels = c("le_hs", "hs", "uni_degree", "grad_degree"), exclude = 0),
            factor(urban, labels = c("rural", "suburban", "urban"), exclude = 0),
            factor(gender, labels = c("male", "female", "other"), exclude = 0),
            factor(engnat, labels = c("yes", "no"), exclude = 0),
            factor(hand, labels = c("right", "left", "both"), exclude = 0),
            factor(religion, labels = c("agnostic", "atheist", "buddhist", "catholic", "mormon",
                                        "protestant", "christian_other", "hindu",
                                        "jewish", "muslim", "sikh", "other"), exclude = 0),
            factor(orientation, labels = c("heterosexual", "bisexual", "homosexual", "asexual",
                                           "other"), exclude = 0),
            factor(race, labels = c("asian", "arab", "black", "misc", "other"), exclude = 0),
            factor(voted, labels = c("yes", "no"), exclude = 0),
            factor(married, labels = c("no", "yes", "divorced"), exclude = 0),
            factor(operatingsystem), factor(browser))
]

# family size wrong - women with most children had 44
dt_bigf[familysize > 44 | familysize == 0, familysize := NA]

# age wrong
dt_bigf[age > 99, age := NA]

# zeros are NAs
names_o <- names(dt_bigf) %>% grep(pattern = "^O", value = TRUE)
dt_bigf[, (names_o) := lapply(.SD, function(col) ifelse(col == 0, NA, col)), .SDcols = names_o]
```

```{r look-at-vcl}
vec_word <- dt_bigf[, sapply(.SD, mean), .SDcols = patterns("^VCL")] %>%
  set_names(c("boat", "incoherent", "pallid", "robot", "audible", "cuivocal", "paucity",
              "epistemology", "florted", "decide", "pastiche", "verdid", "abysmal", "lucid",
              "betray", "funny"))
vec_word[-c(6, 9, 12)]  # true words
vec_word[c(6, 9, 12)]  # made up words
```

```{r make-eloquence}
vcl_fluke <- paste0("VCL", c(6, 9, 12))
dt_bigf[, (vcl_fluke) := lapply(.SD, function(col) as.integer(col == 0)), .SDcols = vcl_fluke]
dt_bigf[, eloquence := rowMeans(.SD), .SDcols = patterns("^VCL")]
```

```{r make-openness}
dt_bigf[, (names_o) := .SD - 1, .SDcols = names_o]

# numbers of missing answers per person (two where all values are missing)
dt_bigf[, O_NA := rowSums(is.na(.SD)), .SDcols = names_o]
dt_bigf[, table(O_NA)]

# 1 question = 4 trials (range 0-4)
dt_bigf[, trials := 40 - 4 * O_NA]
dt_bigf[, table(trials)]

# mark zero trials as missing
dt_bigf[trials == 0, trials := NA]
dt_bigf[, table(trials)]

# binomial data
dt_bigf[!is.na(trials), hits := rowSums(.SD, na.rm = TRUE), .SDcols = names_o]
dt_bigf[, c("misses", "openness") := .(trials - hits, hits / trials)]
```

```{r removing-columns}
dt_bigf[, c(grep("^[ACENOGV]", names(dt_bigf), value = TRUE), "operatingsystem") := NULL]
setcolorder(dt_bigf, neworder = c("introelapse", "testelapse", "surveyelapse", "browser",
                                  "screenw", "screenh", "os", "country", "education", "urban",
                                  "gender", "engnat", "age", "hand", "religion", "orientation",
                                  "race", "voted", "married", "familysize", "eloquence",
                                  "openness", "trials", "hits", "misses"))
```

Blub.

# Analysis of online personality test

## Data

### Overview

```{r data-structure}
str(dt_bigf)
summary(dt_bigf)
```

```{r correlation}
cor(dt_bigf[, -c("hits", "misses", "trials")][, .SD, .SDcols = is.numeric],
    use = "pairwise.complete.obs") %>%
  round(1) %>%
  ggcorrplot::ggcorrplot(method = "circle", type = "lower")
```

### Eloquence score

```{r plot-eloquence, include=TRUE}
dnorm_args <- function(x) list(mean = mean(x, na.rm = TRUE), sd = sd(x, na.rm = TRUE))

ggplot(dt_bigf, aes(x = eloquence)) +
  geom_histogram(aes(y = ..density..), breaks = seq(0, 1, length = 200),
                 color = "black", fill = "white") +
  geom_density() +
  geom_function(fun = dnorm, args = dnorm_args(dt_bigf$eloquence), color = "red")

ggplot(dt_bigf, aes(x = eloquence)) +
  stat_ecdf() +
  geom_function(fun = pnorm, args = dnorm_args(dt_bigf$eloquence), color = "red")
```

### Openness score

```{r plot-openness, include=TRUE, warning=FALSE}
ggplot(dt_bigf, aes(x = openness)) +
  geom_histogram(aes(y = ..density..), breaks = seq(0, 1, length = 200),
                 color = "black", fill = "white") +
  geom_density() +
  geom_function(fun = dnorm, args = dnorm_args(dt_bigf$openness), color = "red")

ggplot(dt_bigf, aes(x = openness)) +
  stat_ecdf() +
  geom_function(fun = pnorm, args = dnorm_args(dt_bigf$openness), color = "red")

ggplot(dt_bigf, aes(sample = openness)) +
  geom_qq() +
  geom_qq_line()
```

### Survey duration

```{r time-spent}
dt_bigf[, summary(.SD), .SDcols = patterns("elapse$")]
```

```{r plot-time, include=TRUE}
# there are some extreme values
ggplot(dt_bigf[introelapse < 3000,], aes(x = introelapse)) +
  geom_histogram(aes(y = ..density..), breaks = seq(1, 3000, length = 100),
                 color = "black", fill = "white")

dt_bigf[, lapply(.SD, function(x) {
            ind_long <- x > 3000
            list(c(sum(!ind_long), mean(x[!ind_long])), c(sum(ind_long), mean(x[ind_long])))
          })
        , .SDcols = patterns("elapse$")]
```

## Pairwise comparisons

```{r todos}
# TODO: scatter plots with openness
# TODO: correlation plots - co-linearity is a problem!
# TODO: contingency tables
# TODO: VCL to one variable
```

<!-- continuous -->

### Openness and eloquence

```{r openness-eloquence, include=TRUE}
ggplot(dt_bigf[!is.na(engnat)], aes(x = eloquence, y = openness)) +
  geom_jitter(height = 0.01, width = 0.01, alpha = 0.5) +
  geom_smooth(aes(color = engnat))
```

### Eloquence and age

```{r eloquence-age, include=TRUE}
ggplot(dt_bigf, aes(x = age, y = eloquence)) +
  geom_jitter(height = 0.01, width = 0.3, alpha = 0.5)
```

### Openness and age

```{r openness-age, include=TRUE}
ggplot(dt_bigf, aes(x = age, y = openness)) +
  geom_jitter(height = 0.01, width = 0.1, alpha = 0.5) +
  geom_smooth()
```

### Openness and family size

```{r openness-familysize, include=TRUE}
ggplot(dt_bigf[familysize < 20,], aes(x = familysize, y = openness)) +
  geom_jitter(height = 0.01, width = 0.35, alpha = 0.5) +
  geom_smooth()
```

<!-- discrete -->

### Openness and country

```{r openness-country, include=TRUE}
ggplot(dt_bigf[(table(country) > 50)[country],], aes(x = country, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and education

```{r openness-education, include=TRUE}
ggplot(dt_bigf[!is.na(education)], aes(x = education, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and urban

```{r openness-urban, include=TRUE}
ggplot(dt_bigf[!is.na(urban)], aes(x = urban, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and gender

```{r openness-gender, include=TRUE}
ggplot(dt_bigf[!is.na(gender),], aes(x = gender, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and engnat

```{r openness-engnat, include=TRUE}
ggplot(dt_bigf, aes(x = engnat, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Eloquence and engnat

```{r eloquence-engnat, include=TRUE}
ggplot(dt_bigf, aes(x = engnat, y = eloquence)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(eloquence, na.rm = TRUE)])
```

### Eloquence and education

```{r eloquence-education, include=TRUE}
ggplot(dt_bigf[!is.na(education),], aes(x = education, y = eloquence)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(eloquence, na.rm = TRUE)])
```

### Age and education

```{r age-education, include=TRUE}
ggplot(dt_bigf[!is.na(education),], aes(x = education, y = age)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(age, na.rm = TRUE)])
```

### Openness and hand

```{r openness-hand, include=TRUE}
ggplot(dt_bigf[!is.na(hand),], aes(x = hand, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and religion

```{r openness-religion, include=TRUE}
ggplot(dt_bigf[(table(religion) > 50)[religion],], aes(x = religion, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and orientation

```{r openness-orientation, include=TRUE}
ggplot(dt_bigf, aes(x = orientation, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and race

```{r openness-race, include=TRUE}
ggplot(dt_bigf, aes(x = race, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and voted

```{r openness-voted, include=TRUE}
ggplot(dt_bigf, aes(x = voted, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])

ggplot(dt_bigf[age > 20], aes(x = voted, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and married

```{r openness-married, include=TRUE}
ggplot(dt_bigf, aes(x = married, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

<!-- technical data -->

```{r duration}
ggplot(dt_bigf[introelapse < 500,], aes(x = introelapse, y = openness)) +
  geom_jitter(height = 0.01, width = 0.00, alpha = 0.5) +
  geom_smooth()

ggplot(dt_bigf[testelapse < 1000,], aes(x = testelapse, y = openness)) +
  geom_jitter(height = 0.01, width = 0.00, alpha = 0.5) +
  geom_smooth()

ggplot(dt_bigf[surveyelapse < 1000,], aes(x = surveyelapse, y = openness)) +
  geom_jitter(height = 0.01, width = 0.00, alpha = 0.5) +
  geom_smooth()
```

```{r browser-os}
ggplot(dt_bigf, aes(x = browser, y = openness)) +
  geom_boxplot()

ggplot(dt_bigf, aes(x = os, y = openness)) +
  geom_boxplot()
```

## Modeling openness score

```{r glm}
# TODO: try centering data
# TODO: dont forget outliers
# TODO: choose a nice reference category
# TODO: variable selection
# TODO: maybe just a normal model
m0 <- glm(cbind(hits, misses) ~ education + gender + urban + engnat + hand + religion +
          orientation + race + voted + married + familysize + eloquence,
          family = quasibinomial(), data = dt_bigf)
summary(m0)
data.table(pred = m0$fitted, val = dt_bigf[as.numeric(names(m0$fitted)), openness]) %$%
  {density(pred) %>% plot()
   density(val) %>% lines(col = "red")}
```

Blub.

# Conclusion

Blub.

<!-- trash -->
```{r first-attempt, eval=FALSE}
dt_bigf[, openness := rowSums(.SD) / 50, .SDcols = patterns("^O")]
0:50 / 50  # possible scores
# dt_bigf[, patterns("^[ACENOG]") := NULL]

ggplot(dt_bigf, aes(x = openness)) +
  geom_histogram(aes(y = ..density..), bins = 100, boundary = 0) +
  geom_function(fun = dnorm, args = list(mean = mean(dt_bigf$openness), sd = sd(dt_bigf$openness))) +
  geom_density(color = "red")

ggplot(dt_bigf, aes(x = openness)) +
  stat_ecdf()
```

