---
title: "Report On Big Five, Assignment 29"
author: "Maximilian Schneider"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
documentclass: report
urlcolor: blue
output:
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    includes:
      in_header: preamble.tex
---

<style>
body {
text-align: justify}
.main-container {
  max-width: 1000px;
  margin-left: auto;
  margin-right: auto;
}
</style>

Abstract

# Introduction

```{r setup, include=FALSE}
# rmarkdown settings
knitr::opts_chunk$set(fig.align = "center", out.width = '80%',
                      include = FALSE, echo = FALSE, cache = FALSE)

# packages
library(data.table)
library(purrr)
library(magrittr)
library(ggplot2); theme_set(theme_bw())

# data
source("R/prepare-data.R")

# functions

# plots
```

Blub.

# Analysis of online personality test

## Data

### Overview

```{r data-structure}
str(dt_bigf)
summary(dt_bigf)
```

```{r correlation}
cor(dt_bigf[, -c("hits", "misses", "trials")][, .SD, .SDcols = is.numeric],
    use = "pairwise.complete.obs") %>%
  round(1) %>%
  ggcorrplot::ggcorrplot(method = "circle", type = "lower")
```

### Eloquence score

```{r plot-eloquence, include=TRUE}
dnorm_args <- function(x) list(mean = mean(x, na.rm = TRUE), sd = sd(x, na.rm = TRUE))

ggplot(dt_bigf, aes(x = eloquence)) +
  geom_histogram(aes(y = ..density..), breaks = seq(0, 1, length = 200),
                 color = "black", fill = "white") +
  geom_density() +
  geom_function(fun = dnorm, args = dnorm_args(dt_bigf$eloquence), color = "red")

ggplot(dt_bigf, aes(x = eloquence)) +
  stat_ecdf() +
  geom_function(fun = pnorm, args = dnorm_args(dt_bigf$eloquence), color = "red")
```

### Openness score

```{r plot-openness, include=TRUE, warning=FALSE}
ggplot(dt_bigf, aes(x = openness)) +
  geom_histogram(aes(y = ..density..), breaks = seq(0, 1, length = 200),
                 color = "black", fill = "white") +
  geom_density() +
  geom_function(fun = dnorm, args = dnorm_args(dt_bigf$openness), color = "red")

ggplot(dt_bigf, aes(x = openness)) +
  stat_ecdf() +
  geom_function(fun = pnorm, args = dnorm_args(dt_bigf$openness), color = "red")

ggplot(dt_bigf, aes(sample = openness)) +
  geom_qq() +
  geom_qq_line()
```

### Survey duration

```{r time-spent}
dt_bigf[, summary(.SD), .SDcols = patterns("elapse$")]
```

```{r plot-time, include=TRUE}
# there are some extreme values
ggplot(dt_bigf[introelapse < 3000,], aes(x = introelapse)) +
  geom_histogram(aes(y = ..density..), breaks = seq(1, 3000, length = 100),
                 color = "black", fill = "white")

dt_bigf[, lapply(.SD, function(x) {
            ind_long <- x > 3000
            list(c(sum(!ind_long), mean(x[!ind_long])), c(sum(ind_long), mean(x[ind_long])))
          })
        , .SDcols = patterns("elapse$")]
```

## Pairwise comparisons

```{r todos}
# TODO: scatter plots with openness
# TODO: correlation plots - co-linearity is a problem!
# TODO: contingency tables
# TODO: VCL to one variable
```

<!-- continuous -->

### Openness and eloquence

```{r openness-eloquence, include=TRUE}
ggplot(dt_bigf[!is.na(engnat)], aes(x = eloquence, y = openness)) +
  geom_jitter(height = 0.01, width = 0.01, alpha = 0.5) +
  geom_smooth(aes(color = engnat))
```

### Eloquence and age

```{r eloquence-age, include=TRUE}
ggplot(dt_bigf, aes(x = age, y = eloquence)) +
  geom_jitter(height = 0.01, width = 0.3, alpha = 0.5)
```

### Openness and age

```{r openness-age, include=TRUE}
ggplot(dt_bigf, aes(x = age, y = openness)) +
  geom_jitter(height = 0.01, width = 0.1, alpha = 0.5) +
  geom_smooth()
```

### Openness and family size

```{r openness-familysize, include=TRUE}
ggplot(dt_bigf[familysize < 20,], aes(x = familysize, y = openness)) +
  geom_jitter(height = 0.01, width = 0.35, alpha = 0.5) +
  geom_smooth()
```

<!-- discrete -->

### Openness and country

```{r openness-country, include=TRUE}
ggplot(dt_bigf[(table(country) > 50)[country],], aes(x = country, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and education

```{r openness-education, include=TRUE}
ggplot(dt_bigf[!is.na(education)], aes(x = education, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and urban

```{r openness-urban, include=TRUE}
ggplot(dt_bigf[!is.na(urban)], aes(x = urban, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and gender

```{r openness-gender, include=TRUE}
ggplot(dt_bigf[!is.na(gender),], aes(x = gender, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and engnat

```{r openness-engnat, include=TRUE}
ggplot(dt_bigf, aes(x = engnat, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Eloquence and engnat

```{r eloquence-engnat, include=TRUE}
ggplot(dt_bigf, aes(x = engnat, y = eloquence)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(eloquence, na.rm = TRUE)])
```

### Eloquence and education

```{r eloquence-education, include=TRUE}
ggplot(dt_bigf[!is.na(education),], aes(x = education, y = eloquence)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(eloquence, na.rm = TRUE)])
```

### Age and education

```{r age-education, include=TRUE}
ggplot(dt_bigf[!is.na(education),], aes(x = education, y = age)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(age, na.rm = TRUE)])
```

### Openness and hand

```{r openness-hand, include=TRUE}
ggplot(dt_bigf[!is.na(hand),], aes(x = hand, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and religion

```{r openness-religion, include=TRUE}
ggplot(dt_bigf[(table(religion) > 50)[religion],], aes(x = religion, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and orientation

```{r openness-orientation, include=TRUE}
ggplot(dt_bigf, aes(x = orientation, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and race

```{r openness-race, include=TRUE}
ggplot(dt_bigf, aes(x = race, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and voted

```{r openness-voted, include=TRUE}
ggplot(dt_bigf, aes(x = voted, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])

ggplot(dt_bigf[age > 20], aes(x = voted, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

### Openness and married

```{r openness-married, include=TRUE}
ggplot(dt_bigf, aes(x = married, y = openness)) +
  geom_boxplot() +
  geom_hline(yintercept = dt_bigf[, median(openness, na.rm = TRUE)])
```

<!-- technical data -->

```{r duration}
ggplot(dt_bigf[introelapse < 500,], aes(x = introelapse, y = openness)) +
  geom_jitter(height = 0.01, width = 0.00, alpha = 0.5) +
  geom_smooth()

ggplot(dt_bigf[testelapse < 1000,], aes(x = testelapse, y = openness)) +
  geom_jitter(height = 0.01, width = 0.00, alpha = 0.5) +
  geom_smooth()

ggplot(dt_bigf[surveyelapse < 1000,], aes(x = surveyelapse, y = openness)) +
  geom_jitter(height = 0.01, width = 0.00, alpha = 0.5) +
  geom_smooth()
```

```{r browser-os}
ggplot(dt_bigf, aes(x = browser, y = openness)) +
  geom_boxplot()

ggplot(dt_bigf, aes(x = os, y = openness)) +
  geom_boxplot()
```

## Modeling openness score


* TODO: try centering data
* TODO: dont forget outliers
* TODO: choose a nice reference category
* TODO: variable selection
* TODO: maybe just a normal model

```{r glm}
dt_bigf.na_omit <- na.omit(dt_bigf, cols = c("education", "gender", "urban", "engnat", "hand",
                                             "religion", "orientation", "race", "voted", "married",
                                             "familysize", "eloquence"))

m0 <- glm(cbind(hits, misses) ~ education + gender + urban + engnat + hand + religion +
          orientation + race + voted + married + familysize + eloquence,
          family = quasibinomial(), data = dt_bigf.na_omit)
summary(m0)
```

```{r lm}
m1 <- lm(openness ~ education + gender + urban + engnat + hand + religion + orientation + race +
         voted + married + familysize + eloquence, data = dt_bigf.na_omit)
summary(m1)
```

```{r plot-model-predictions}
rbind(
  data.table(pred = m0$fitted, val = dt_bigf[as.numeric(names(m0$fitted)), openness], m = "0"),
  data.table(pred = m1$fitted, val = dt_bigf[as.numeric(names(m1$fitted)), openness], m = "1")
) %>%
  ggplot(aes(x = val, y = pred, color = m)) +
  geom_point() +
  geom_smooth()
```

```{r variable-selection}
m_const <- lm(openness ~ 1, data = dt_bigf.na_omit)

m1.sel_both <- step(m1, direction = "both", k = log(nrow(dt_bigf.na_omit)))
m1.sel_forward <- step(m1, scope = list(lower = m_const, upper = m1),
                       direction = "forward", k = log(nrow(dt_bigf.na_omit)))
m1.sel_backward <- step(m1, direction = "backward", k = log(nrow(dt_bigf.na_omit)))

summary(m1.sel_both)
summary(m1.sel_forward)
summary(m1.sel_backward)
```

```{r}
```

Blub.

# Conclusion

Blub.

<!-- trash -->
```{r first-attempt, eval=FALSE}
dt_bigf[, openness := rowSums(.SD) / 50, .SDcols = patterns("^O")]
0:50 / 50  # possible scores
# dt_bigf[, patterns("^[ACENOG]") := NULL]

ggplot(dt_bigf, aes(x = openness)) +
  geom_histogram(aes(y = ..density..), bins = 100, boundary = 0) +
  geom_function(fun = dnorm, args = list(mean = mean(dt_bigf$openness), sd = sd(dt_bigf$openness))) +
  geom_density(color = "red")

ggplot(dt_bigf, aes(x = openness)) +
  stat_ecdf()
```

